Growing Up with Nell: A Narrative Interface for Literacy

### 2012-03-12 paper.tex
Tweaks to TurtleScript section.

We have developed a block-oriented view of JavaScript, which we call
TurtleScript (Figure~\ref{fig:turtlescript}).  Combined with subsets of JavaScript
for learners, this allows us to use TurtleScript as the single
implementation language for Nell.  TurtleScript scales from Logo-like
pedagogical tasks up to the implementation of TurtleScript and the
Nell system itself.  TurtleScript's block view is isomorphic to
JavaScript's standard textual
representation, which preserves the code-reading skills of existing
programmers.  We have begun implementation of a
tablet programming environment for TurtleScript which uses
drag-and-drop, direct interaction, and intelligent prompting to reduce
text entry requirements.

% XXX refer to TurtleScript excerpt in figure somewhere here.
\begin{figure}
\centering
\epsfig{file=turtlescript.eps, height=1.5in}
\caption{Factorial function in TurtleScript~\cite{turtlescript}.}\label{fig:turtlescript}
\end{figure}

>>>>

We have developed a block-oriented view of JavaScript, which we call
TurtleScript~\cite{turtlescript}.  This allows us to use
the TurtleScript view of JavaScript as the single
implementation language for Nell.  TurtleScript scales from Logo-like
pedagogical tasks (in subsets of the language) up to the
implementation of TurtleScript and the
Nell system itself.  TurtleScript's block view is isomorphic to
JavaScript's standard textual
representation to preserve the code-reading skills of existing
programmers (Figure~\ref{fig:turtlescript}).  We have begun implementation of a
tablet programming environment for TurtleScript which uses
drag-and-drop, direct interaction, and intelligent prompting to reduce
text entry requirements.

% XXX refer to TurtleScript excerpt in figure somewhere here.
\begin{figure}
\centering
\epsfig{file=turtlescript.eps, height=1.5in}
\caption{Factorial function in TurtleScript.}\label{fig:turtlescript}
\end{figure}
